---
title: "Heywood's Questions"
Author: "Heywood  Williams-Tracy"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(tidyr)
library(gclus)
library(gganimate)
library(ggpubr)
library(vctrs)
library(corrplot)
library(reshape2)
library(ggheatmap)
library(PerformanceAnalytics)
```


```{r, echo=F}
# Load the data
golden_leaf_data <- read.csv("final_data_with_golden_leaf.csv")
```
`
#### RQ1: What trends exist in the data?
```{r, echo=F}
# Find the average amount of funds awarded per town
average_funds_awarded <- golden_leaf_data %>% group_by(Applicant) %>% summarise(average_funds_awarded = mean(Grant.Award....))
average_funds_awarded
```
```{r, echo=F}
correlation_variables <- cor(golden_leaf_data[c("Total.Population", "Living.in.Poverty", "Median.Household.Income..In.2020.Inflation.Adjusted.Dollars.")])

corrplot(correlation_variables, method = "circle")
```

```{r, echo=F}
# Correct the column types
#golden_leaf_data <- char_to_float(golden_leaf_data, "Award.Date")
#golden_leaf_data <- char_to_float(golden_leaf_data, "Application.Date")

# Find the average difference in time between the application and the award
#average_time <- golden_leaf_data %>% group_by(Applicant) %>% summarise(Time.between.application.and.award = "Award.Date" - "Application.Date") %>% summarise(average_time = mean(Time.between.application.and.award))
```

#### What variables influence whether an organization receives funding?
```{r, echo=F}
# Remove rows with missing values in Grant Award column
simplified_data <- golden_leaf_data[complete.cases(golden_leaf_data$Grant.Award....),]

cor_data = simplified_data[c("Total.Population", "Living.in.Poverty", "Median.Household.Income..In.2020.Inflation.Adjusted.Dollars.", "Grant.Award....")]

#head(cor_data)

chart.Correlation(cor_data, histogram=TRUE, method = "pearson")
```


#### To what extent is there equitable distribution of funds?
```{r, echo=T}
# Find the average amount of funds awarded per race
white_cor = cor(simplified_data$Grant.Award...., simplified_data$White.Alone)
african_american_cor = cor(simplified_data$Grant.Award...., simplified_data$Black.or.African.American.Alone)
native_american_cor = cor(simplified_data$Grant.Award...., simplified_data$American.Indian.and.Alaska.Native.Alone)
asian_cor = cor(simplified_data$Grant.Award...., simplified_data$Asian.Alone)
pi_cor = cor(simplified_data$Grant.Award...., simplified_data$Native.Hawaiian.and.Other.Pacific.Islander.Alone)
other_race_cor = cor(simplified_data$Grant.Award...., simplified_data$Some.Other.Race.Alone)
two_or_more_cor = cor(simplified_data$Grant.Award...., simplified_data$Two.or.More.Races)
white_non_hispanic_cor = cor(simplified_data$Grant.Award...., simplified_data$White.Alone..Not.Hispanic.or.Latino.Homeowners.)

cat(white_cor, african_american_cor, native_american_cor, asian_cor, pi_cor, other_race_cor, two_or_more_cor, white_non_hispanic_cor)
```

#### How does flood risk correlate with the amount of funds received if any?
```{r, echo=T}
cor(simplified_data$Grant.Award...., simplified_data$Total.Percent.of.Land.at.Some.Level.of.Flood.Risk)
```
#### RQ3: Is there a correlation between race/socioeconomic status and applying for funding?
```{r, echo=T}
cor(simplified_data$Grant.Award...., simplified_data$White.Alone..Not.Hispanic.or.Latino.Homeowners.)
```
#### RQ4: What is the average amount of funds awarded if any?
```{r, echo=T}
mean_funding = mean(simplified_data$Grant.Award....)
cat("The average amount of funds awarded is", mean_funding)
```

#### RQ5: What distribution does the amount of funds awarded follow if any?
```{r, echo=T}
ggplot(simplified_data, aes(x = Grant.Award....)) +
  geom_histogram(binwidth = 0.99, color = "red", fill = "white") + ylim(0, 100) #+ xlim(0, 10000)
```

#### RQ6: Is there a correlation between the size of the town and the amount of funds awarded?
```{r, echo=T}
# Plot of the amount of funds awarded and the population of the town and limit the data to towns with a population of 1000 or less
ggplot(golden_leaf_data, aes(x = Total.Population, y = Grant.Award....)) + geom_point() + geom_smooth(method = "lm") + xlim(0, 100000)
```
```
